Stability of variational quantum dynamics with Gaussian approximants

### 2013-06-28 paper.tex
Fitting states with randomly drawn initial guesses

>>>>

When physicists began to study quantum mechanics, they could hardly have avoided discovering coherent states.  When they grasped that observables were inherently uncertain and considered laws of probability, the normal distribution sprung to mind at once.  Once they understood the dynamics of the free particle, and looked for a more interesting system to study, the obvious choice was the harmonic oscillator.  The first question was its ground state; the second was why, in the classical limit, it oscillated.  Coherent states were the answer to both.

Variational mechanics was another obvious idea.  The quantum equations of motion were hard to solve exactly, except for some very simple systems.  It was known from very early on that the solutions were extema of certain properties: ground states had the lowest possible energy, trajectories the least possible action.  So it was natural to consider a class of possible solutions that could be treated exactly, and find out which of them had the extreme value over the class.

In the 1970s, Heller put the two ideas together, and proposed
